I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-12-02 paper_io_sim.tex

			where:
			\begin{itemize}
				\item $t_{r}$ is the data read time
				\item $t_{w}$ is the data write time
				\item $D$ is the amount of data to read/write
				\item $b_r$ is the read bandwidth of the device
				\item $b_w$ is the write bandwidth of the device
			\end{itemize}

			Since bandwidth sharing was not simulated, this prototype did not support 
			concurrency: it was limited to single-threaded pipelines running on systems 
			with a single-core CPU. We used it in a first validation of our simulation 
			model, against a real sequential pipeline running on a real system.
			Source code of our Python prototype is available at 
            \url{https://github.com/big-data-lab-team/paper-io-simulation/tree/master/exp/pysim}

@@

			The I/O time of tasks in simulators and real execution is also tracked and compared. 
			Figure~\ref{fig:single_errors} shows the relative error of simulated I/O time 
			of individual I/O activities. 
			Our pipeline consists of 3 tasks, and each task reads an input file, 
			performs some computation, and writes output file. 
			Thus, there are 6 sequential I/O activities, \textit{Read 1} and \textit{Write 1} 
			from the first task, \textit{Read 2} and \textit{Write 2} the second task, 
			and \textit{Read 3}, \textit{Write3} from the last task.

@@

			Our short term future work will be re-evaluate the model with asymmetrical 
			disk bandwidths that will be released in the next SimGrid version.
			The next step is to study the detail in cache eviction mechanism to make 
			the our simulation results closer to reality. 
			Another point that needs to be further improved is the ability to configure  
			different anonymous memory usage levels of applications since it affects  
			the amount of cache used.
			We also plan to support random I/O and file readahead, as well as 
			saving and restoring disk state when hosts are turned on/off.

>>>>

			where:
			\begin{itemize}
				\item $t_{r}$ is the data read time
				\item $t_{w}$ is the data write time
				\item $D$ is the amount of data to read or write
				\item $b_r$ is the read bandwidth of the device
				\item $b_w$ is the write bandwidth of the device
			\end{itemize}

			Since bandwidth sharing was not simulated, this prototype does not support 
			concurrency: it is limited to single-threaded pipelines running on systems 
			with a single-core CPU. We used it in a first validation of our simulation 
			model, against a real sequential pipeline running on a real system.
			The source code of our Python prototype is available at 
			\url{https://github.com/big-data-lab-team/paper-io-simulation/tree/master/exp/pysim}

@@

			The I/O time of tasks in simulators and real execution is also tracked and compared. 
			Figure~\ref{fig:single_errors} \tristan{wrong reference} shows the relative error of simulated I/O time 
			of individual I/O activities. 
			Our pipeline consists of 3 tasks, and each task reads an input file, 
			performs some computation, and writes output file. 
			Thus, there are 6 sequential I/O activities, \textit{Read 1} and \textit{Write 1} 
			from the first task, \textit{Read 2} and \textit{Write 2} the second task, 
			and \textit{Read 3}, \textit{Write3} from the last task.

@@

			Our short term future work will be re-evaluate the model with asymmetrical 
			disk bandwidths that will be released in the next SimGrid version.
			The next step is to study the detail in cache eviction mechanism to achieve 
			better simulation results. 
			We also plan to support random I/O and file readahead, as well as 
			saving and restoring disk state when hosts are turned on/off.
